\documentclass[12pt]{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
 
\name{Henry Umansky}
\address{6 Colton Ct \\ Hamilton, NJ 08619}
\address{humansky@gmail.com \\ (267) 408-7622}
 
\begin{document}

\begin{rSection}{Overview}
Highly motivated and dedicated Information Technology professional capable of building and managing complex projects from concept to completion. Team player with an excellent eye for detail, an ability to manage projects on time and under budget, as well as identify and address potential obstacles along the way. Experienced leader, managing several web application and software projects spanning over 15 years, ready to share knowledge, collaborate, and face new challenges. Looking for a similiarly motivated organization that shares my love and passion for new and emerging digital technology.
\end{rSection}

\begin{rSection}{Experience}

\begin{rSubsection}{Princeton University}{2009-present}{Manager, Web Programming}{Princeton, NJ}{My primary responsibilities include managing and mentoring the team of developers for the University's Web Development Services group, in order to deliver high-quality digital solutions that align with the University's strategic and academic needs. Responsibilities include all aspects of Web site development: such as project management, content strategy, application coding, automated testing, deployment, documentation, maintenance, and system administration using a combination of secure coding best practice and productivity tools. In addition, I provide training and support to members of the University who use our Drupal or WordPress Content Management System. Other major responsibilities include:}
\item Help define and document standards and best practices regarding development processes.
\item Managing performance and professional development for the team members.
\item Identify and analyze business requirements, while defining and estimating SMART tasks.
\item Aligning development efforts with the University's mission, business strategy, customer's needs and project's goals.
\item Working closely with all stakeholders to ensure development work is delivered on time and within scope.
\item Collaborating with the group’s developers, designers and content strategists in order to create information architecture, wireframes and functional specifications.
\item Partnering with other internal groups to ensure the technical needs of our services are met.
\item Abilitiy to effectively scale and work iteratively, regardless of the size and scope of the project, using an Agile project management framework.
\item Provide end-user support and training through various channels: online, phone or in-person.
\item Passion for learning and strivng to stay ahead of the proverbial S-curve of the ever-changing digital landscape.
\item Maintaining positive relationships with all constituents and stakeholders.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Princeton University}{2008-2009}{Senior Web Developer }{Princeton, NJ}{My primary responsibilities consisted all aspects of Web site development, including application coding, testing and deployment, maintenance, upkeep using a combination of coding and productivity tools, and project management. Other major responsibilities include: }
\item Lead web application development and support for OIT's Web Development Services group, working in collaboration with other groups within OIT.
\item Help define and document standards and best practices regarding development processes.
\item Help identify and analyze project requirements and tasks.
\item LProvide end-user technical support and documentation.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Princeton University}{2006-2008}{Web Developer/Designer}{Princeton, NJ}{My primary responsibilities consisted of providing web development, design and support for the Office of Information Technology's New Media Center, working in close collaboration with the University's Office of Communication. Other major responsibilities include:}
\item Web site development, maintenance, and design graphics using a combination of coding and productivity tools.
\item Install, configure and troubleshoot a variety of desktop computing applications, networking applications, and information access tools in a heterogeneous environment.
\item Maintain and manage the University's New Media Center Digital Lab.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Misha of Siberia Inc}{2004-2006}{Independent Consultant}{Philadelphia, PA}{My primary responsibilities consisted of:}
\item Application design and system administrator.
\item Setup and maintenance of several Linux servers, including web, email, VPN, and DNS server.
\item Designed and implemented an invoice, inventory tracking, A/R, A/P, receipt software using VB.NET and Microsoft SQL Server.
\item Implemented a stand-alone Virtual PBX telecommunication system using open-source Asterisk software and Cisco VoIP hardware.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{University of Pittsburgh}{2001-2004}{Systems Programmer III}{Pittsburgh, PA}{My primary responsibilities consisted of: web-based software development, systems administration, and provision of technical support to the University community. In addition to the able responsibilities I also assisted in providing outstanding customer service to the University community. I helped to support a diverse customer base on a large number of platforms including Solaris, Linux, Mac OS, and Windows. I also assisted in supporting customers on Network and Telecommunications related issues. I was also responsible for the deployment of several Linux-based web/database servers for use by the University Technology Help Desk. These servers provide a number of web based applications that allow Help Desk analysts to perform their jobs more efficiently and access information that is vital to their providing quality customer service. These applications include:}
\item A web based tool allowing analysts to quickly and easily respond to a large volume of support requests via email.
\item An authorization system to allow/deny access to certain areas of the internal Help Desk website for specific users and groups. I also developed a web based front-end for this security system to allow administrators to create users and groups and assign rights to those users/groups.
\item A set of scripts to streamline reporting on Help Desk call/ticket statistics. These scripts are responsible for extracting data from a variety of sources, formatting that data, and importing that data into a large centralized database.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & PHP, Ruby, Python, XML/XSL, HTML, CSS, JavaScript, C, C++, Java, Perl \\
Web CMS and Frameworks & Drupal, Zend, Symfony, NodeJS, JQuery \\
Databases & MySQL, PostgreSQL, SQLite, MongoDB, Redis, Memcache \\
Tools & Git, Grunt, Capistrano, Jenkins, Apache, Nginx, Varnish, Puppet, Ansible, Vagrant
\end{tabular}

\end{rSection}

\begin{rSection}{Education}
{\bf Columbia University} \hfill {\em December 2016} \\
Executive Masters in Technology Management \\
{\bf University of Pittsburgh} \hfill {\em June 2004} \\
Bachelor of Science in Computer Science \\
\end{rSection}

\begin{rSection}{Awards \& Certificates}
\begin{tabular}{@{} >{\bfseries}l @{\hspace{2ex}} l }
September 2012 & \textit{Zend PHP 5.3 Certified Engineer} \\
November 2010 & \textit{Princeton University Management Development Certificate} \\
August 2010 & \textit{ITIL v3 Foundation Certificate} \\
February 2008 & \textit{Office of Information Technology Service Award} \\
September 2007 & \textit{Office of Information Technology Service Award} \\
June 2007 & \textit{Princeton University Information Technology Achievement Award} \\
\end{tabular}
\end{rSection}

\begin{rSection}{References}
Available upon request
\end{rSection}

\end{document}
